Carrier phase and amplitude estimation for phase shift keying using pilots and data (Appendix)

### 2012-08-22 paper2.tex
minor edits to second paper.

\begin{lemma}\label{lem:maxineq}(Maximal inequalities)
Suppose $X_1, \dots, X_N$ are zero mean Gaussian random variables each with variance less than some positive constant $K$.  Then
\[
\expect \sup_{n = 1, \dots, N} \abs{X_n} \leq 3  \sqrt{K \log N}
\]
where $\log N$ is the natural logarithm of $N$.
\end{lemma}
\begin{IEEEproof}
This result is well known, see for example~\cite[Section 3]{Pollard_asymp_empi_proc_1989}  
\end{IEEEproof}

\begin{lemma}\label{lem:metricentropy}(Covering numbers)
For $k \in \ints$ there exists a discrete set $T_\epsilon(k) \subset B_\epsilon$ with the property that, for every $\lambda \in B_\epsilon$, there is a $\lambda_1$ and $\lambda_2$ in $T_\epsilon(k)$ such that the psuedometric
\[
d_1(\lambda, \lambda_1) = \sum_{i \in P \cup D} \big( f_{i}(\lambda) - f_{i}(\lambda_1) \big)^2 \leq 2^{-k} C_\epsilon L,
\]
and the psuedometric
\[
d_2(\lambda, \lambda_2) = \sum_{i \in P \cup D} \sabs{f_{i}(\lambda) - f_{i}(\lambda_2)} \leq 2^{-k} D_\epsilon L,
\]
where $C_\epsilon$ and $D_\epsilon$ are defined in~\eqref{eq:Cepsdefn} and~\eqref{eq:Depsdefn}.  The number of elements in $T_\epsilon(k)$ is no more than $K_3 2^{k}$ where $K_3$ is a positive constant, independent of $L$, $\epsilon$ and $k$.
\end{lemma}
\begin{IEEEproof}

>>>>

\begin{lemma}\label{lem:maxineq}(Maximal inequalities)
Suppose $X_1, \dots, X_N$ are zero mean Gaussian random variables each with variance less than some positive constant $K$, then
\[
\expect \sup_{n = 1, \dots, N} \abs{X_n} \leq 3  \sqrt{K \log N}
\]
where $\log N$ is the natural logarithm of $N$.
\end{lemma}
\begin{IEEEproof}
This result is well known, see for example~\cite[Section 3]{Pollard_asymp_empi_proc_1989}  
\end{IEEEproof}

\begin{lemma}\label{lem:metricentropy}(Covering numbers)
For $k \in \ints$ there exists a discrete set $T_\epsilon(k) \subset B_\epsilon$ with the property that, for every $\lambda \in B_\epsilon$, there is a $\lambda_1$ and $\lambda_2$ in $T_\epsilon(k)$ such that the psuedometric
\[
d_1(\lambda, \lambda_1) = \sum_{i \in P \cup D} \big( f_{i}(\lambda) - f_{i}(\lambda_1) \big)^2 \leq 2^{-k} C_\epsilon L,
\]
and the psuedometric
\[
d_2(\lambda, \lambda_2) = \sum_{i \in P \cup D} \sabs{f_{i}(\lambda) - f_{i}(\lambda_2)} \leq 2^{-k} D_\epsilon L,
\]
where $C_\epsilon$ and $D_\epsilon$ are defined in~\eqref{eq:Cepsdefn} and~\eqref{eq:Depsdefn}.  The number of elements in $T_\epsilon(k)$ is no more than $K_3 2^{k}$ where $K_3$ is a positive constant, independent of $L$, $\epsilon$ and $k$.
\end{lemma}
\begin{IEEEproof}
% We will first construct a set $T^2_\epsilon(k)$ containing no more than $K_{23}2^{k}$ elements and so that for every $\lambda \in B_\epsilon$ there exists $\lambda_2 \in T^2_\epsilon(k)$ such that $d_2(\lambda, \lambda_2) \leq 2^{-k} D_\epsilon L$ with $K_{23}$ a constant, independent of $L$, $\epsilon$ and $k$.  Using a similar construction we find a set $T^1_\epsilon(k)$ containing no more than $K_{13}2^{k}$ elements and so that for every $\lambda \in B_\epsilon$ there exists $\lambda_1 \in T^1_\epsilon(k)$ such that $d_1(\lambda, \lambda_2) \leq 2^{-k} D_\epsilon L$ with $K_{13}$ a constant, independent of $L$, $\epsilon$ and $k$.  Puting $T_\epsilon(k) = T^1_\epsilon(k) \cup T^2_\epsilon(k)$ will then complete the proof with $K_3 = K_{13} + K_{23}$.

% We will only give a construction for $T^2_\epsilon(k)$, the construction for $T^1_\epsilon(k)$ being similar.  First observe that
% \[
% f_{i}(\lambda) - f_{i}(\lambda_2) = \begin{cases}
% R_i\big( \sin(\lambda + \Phi_i) - \sin(\lambda_2 + \Phi_i) \big) & i \in P \\
% R_i\big(\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\lambda_2 + \Phi_i}\big) & i \in D
% \end{cases}
% \]
% Let 
% \[
% U = \{\epsilon(\ell 2^{-k} - 1) \mid \ell = 0, 1, \dots, 2^{k+1} \} 
% \]
% be a set containing $2^{k+1} + 1$ elements uniformly spaced over $B_\epsilon$.  For every $\lambda \in B_\epsilon$ there exists a $\lambda^* \in U$ such that $\abs{\lambda - \lambda^*} < \epsilon 2^{-k}$.  Since $\sin(\cdot)$ is Lipshitz continuous with constant $K=1$, it follows that if $i \in P$ then,
% Let 
% \begin{align*}
% \abs{f_{i}(\lambda) - f_{i}(\lambda_2)} &= R_i\abs{ \sin(\lambda + \Phi_i) - \sin(\lambda^* + \Phi_i) } \\
% &\leq R_i\sabs{\lambda - \lambda^*} \\
% &< \epsilon 2^{-k} R_i.
% \end{align*}
% Thus
% \[
% \sum_{i \in P} \sabs{f_{i}(\lambda) - f_{i}(\lambda^*)} < \epsilon 2^{-k} \sum_{i\in P} R_i.
% \]
% As in Lemma~\ref{lem:epslmlemma} let $S = \{ i \in D \mid I_\epsilon(\Phi_i) \}$. Now, if $i \in D$ but $i \notin S$ then 
% \[
% \round{\lambda + \Phi_i} = \round{\lambda^* + \Phi_i} = \round{\Phi_i},
% \] 
% so
%  \begin{align*}
%  \vert f_{i}(\lambda) - &f_{i}(\lambda^*)\vert \\
% &= R_i\vert\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\lambda^* + \Phi_i}\vert \\
%  &= R_i\vert\sin(\lambda + \Phi_i - \round{\Phi_i}) - \sin(\lambda^* + \Phi_i - \round{\Phi_i})\vert  \\
%  &\leq R_i \sabs{\lambda - \lambda^*} \\
% &< \epsilon 2^{-k} R_i.
%  \end{align*}
% Thus,
% \[
% \sum_{i \in D, i \notin S} \sabs{f_{i}(\lambda) - f_{i}(\lambda^*)} < \epsilon 2^{-k} \sum_{i \in D, i \notin S} R_i 
% \]

% To handle the case when $i \in S$ we need to add some extra elements to the set $U$.  Let 
% \[
% r_i = \begin{cases}
% \tfrac{\pi}{M} - \fracpart{\Phi_i} & \fracpart{\Phi_i} > 0 \\
% -\tfrac{\pi}{M} - \fracpart{\Phi_i} & \fracpart{\Phi_i} \leq 0
% \end{cases}
% \]
% and let $\sigma$ be a permutation of the indices in $S$ such that $r_i$ are in ascending order, that is,
% \begin{equation}\label{eq:sigmasortind}
% r_{\sigma(i)} \leq r_{\sigma(k)}
% \end{equation}
% whenever $i < k $ where $i, k \in \{0, 1, \dots, \abs{S}-1\}$.  Now,
% \begin{align*}
% \sum_{i\in S} \sabs{f_{i}(\lambda) - f_{i}(\lambda^*)} = \sum_{i = 0}^{\abs{S}-1} \sabs{ f_{\sigma(i)}(\lambda) - f_{\sigma(i)}(\lambda^*)}.
% \end{align*}
% If $\epsilon > \lambda \geq r_{\sigma(k)} > 0$ for some $k$, then
% \[
% \round{\lambda + \fracpart{\Phi_{\sigma(i)}}} = \round{\lambda + \tfrac{\pi}{M} - r_{\sigma(i)}} = \tfrac{\pi}{M}
% \]
% for all $i \leq k$, whilst
% \[
% \round{\lambda + \fracpart{\Phi_{\sigma(i)}}} = \round{\lambda + \tfrac{\pi}{M} - r_{\sigma(i)}} = 0
% \]
% for all $i > k$.  Otherwise if $-\epsilon < \lambda < r_{\sigma(k)} \leq 0$ for some $k$, then
% \[
% \round{\lambda + \fracpart{\Phi_{\sigma(i)}}} = \round{\lambda + -\tfrac{\pi}{M} - r_{\sigma(i)}} = -\tfrac{\pi}{M}
% \]
% for all $i \leq k$, whilst
% \[
% \round{\lambda + \fracpart{\Phi_{\sigma(i)}}} = \round{\lambda + \tfrac{\pi}{M} - r_{\sigma(i)}} = 0
% \]
% for all $i > k$.

% Let $R = \sum_{i \in S} R_i$ and let $d(\ell)$ be the largest integer such that
% \[
% \sum_{i=0}^{d(\ell)} R_{\sigma(i)} \leq \frac{\ell}{2^k} R.
% \]
% for integers $\ell = 1, \dots, 2^k$.  Define the intervals
% \[
% L_\ell = \in [r_{d(\ell)}, r_{d(\ell+1)})
% \]
% where $r_{0} = -\epsilon$ and $r_{2^k+1} = \epsilon$.  Then $L_0, L_1, \dots, L_{2^k}$ partition the closure of $B_\epsilon$.  If $\lambda$ and $\lambda^*$ are from interval $L_\ell$, then for all $i \in \{0, 1, \dots, \abs{S}-1\}$ less than $d(\ell)$,
% \begin{align*}
% \fracpart{\lambda + \Phi_{\sigma(i)}} &= \fracpart{\lambda + \fracpart{\Phi_{\sigma(i)}}} \\
% &= \fracpart{\lambda + \fracpart{\Phi_{\sigma(i)}}}
% \end{align*}
% \begin{align*}
% \vert f_{\sigma(i)}(\lambda) - &f_{\sigma(i)}(\lambda^*) \vert \\
% &= R_{\sigma(i)}\vert\sin\fracpart{\lambda + \Phi_{\sigma(i)}} - \sin\fracpart{\lambda^* + \Phi_{\sigma(i)}}\vert 
% \end{align*}
BLERG
